Dark matter halo shapes in the Auriga simulations

### 2019-08-21 Document/paper.tex
edit

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{angles_alignment_MHD.pdf}
\end{center}
\caption{Angles between the principal axis of the dark matter halo
  shape and the angular momentum of the stellar disc 
  as a function of the radius at
  which the halo shape directions are measured.
  Each panel compares the alignment of the corresponding
  major, middle, and minor axis in the halo.
  Thin lines correspond to each one of the thirty halos in the sample
  while the thick line traces the median value as a function of  radius.
  The sample presents a good alignment of the angular
  momentum with the minor halo axis. 
  This alignment is also constant in radius.
  However, the dark matter shells twist significantly in $6$ halos 
  of our sample making the alignment measurement change. 
}
\label{fig:cumulative_alignment}
\end{figure*}

@@

Figure~\ref{fig:alignment_correlations} shows the correlation between
the twisting at the four different radii at which we have measured the
alignments. The median, mean and standard deviation of the twisting 
are $2$, $6$ and $8$ degrees, respectively.
The correlation between twisting and triaxiality also changes with
radius as measured by the Spearman's rank correlation coefficient.
The largest correlation is obtained for the halo triaxiality measured at
$0.12R_{200}$. 
The most important consequence of this changing degree in correlation
is that twisting cannot be explained only by large triaxiality values
and a possibly noisy determination of the shape axis.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{angles_alignment_MHD.pdf}
\end{center}
\caption{Angles between the principal axis of the dark matter halo
  shape and the angular momentum of the stellar disc 
  as a function of the radius at
  which the halo shape directions are measured.
  Each panel compares the alignment of the corresponding
  major, middle, and minor axis in the halo.
  Thin lines correspond to each one of the thirty halos in the sample
  while the thick line traces the median value as a function of  radius.
  The sample presents a good alignment of the angular
  momentum with the minor halo axis. 
  This alignment is also constant in radius.
  However, the dark matter shells twist significantly in six halos 
  of our sample making the alignment change. 
}
\label{fig:cumulative_alignment}
\end{figure*}

@@

Figure~\ref{fig:alignment_correlations} shows the correlation between
the twisting and the corresponding triaxiality at the four different
radii at which the shape directions are measured.
The median, mean and standard deviation of the twisting 
are $2$, $6$ and $8$ degrees, respectively.
The correlation between twisting and triaxiality also changes with
radius as measured by the Spearman's rank correlation coefficient.
The largest correlation is obtained for the halo triaxiality measured at
$0.12R_{200}$. 
The most important consequence of this changing degree in correlation
is that twisting cannot be explained only by large triaxiality values
and a possibly noisy determination of the shape axis.
